Network Analysis of Code Similarity

### 2015-02-07 network-analysis.Rmd
Fix NY
Minor changes to networks

```{r echo=FALSE}
packrat::on()
library(magrittr)
library(RWeka)
library(stringi)
library(igraph)
source("R/helper.R")

@@

significance_threshold <- 0.03
cf2[cf2 < significance_threshold] <- NA
cf2[is.na(cf2)] <- 0
```

@@

```{r}
g <- graph.adjacency(cf2, mode = "directed", weighted = TRUE, diag = FALSE) 
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar=c(0,0,1,0))
plot(g, edge.width = E(g)$weight * 10, layout = l,
     edge.arrow.size= 0.15, vertex.size = 5)
title("Codes of Civil Procedure")
```

@@

```{r}
ny <- which(V(g)$name == "IA851")
neighbors(g, ny)
graph.neighborhood(g, order = 1, nodes = ny)[[1]] %>%
  plot_graph()
```

>>>>

```{r echo=FALSE}
packrat::on()
library(magrittr)
library(RWeka)
library(stringi)
library(igraph)
library(d3Network)
source("R/helper.R")

@@

significance_threshold <- 0.25
cf2[cf2 < significance_threshold] <- NA
cf2[is.na(cf2)] <- 0
```

@@

```{r fig.width=10, fig.height=10}
g <- graph.adjacency(cf2, mode = "directed", weighted = TRUE, diag = FALSE) 
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar=c(0,0,1,0))
plot(g, edge.width = E(g)$weight * 8, layout = l,
     edge.arrow.size= 0.15, vertex.size = 5)
title("Codes of Civil Procedure")
```

@@

```{r}
ny <- which(V(g)$name == "NY1850")
neighbors(g, ny)
graph.neighborhood(g, order = 1, nodes = ny)[[1]] %>%
  plot_graph()
```
